Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of neutron star - black hole binary observations

### 2016-09-03 Paper/paper.tex
s3 smoothened

Past (and future) efforts with Advanced LIGO have used (or plan to use) BHBH

@@

We inject LEA+ NSBH signals into zero noise, and run an MCMC sampler on
them using equivalent BBH templates (same model, tidal terms $\rightarrow 0$).
We fix $\mns=1.35M_\odot$ and $\chins=0$, and explore a range of nuclear
equations of state via the single tidal deformability parameter
$\lambdans\in\{500, 800, 1000, 1500, 2000\}$. Our injections also span a
hypercubic regular grid in the BH parameter space, with vertices at
$q\in\{2,3,4,5\}$, i.e.
$\mbh\in\{2.7M_\odot, 4.05M_\odot, 5.4M_\odot, 6.75M_\odot\}$, and BH spins
$\chibh\in\{-0.5, 0, +0.5, +0.75\}$. 
Finally, we sample all other source-related parameters that determine the
signal strength but not character\footnote{For aligned-spin signals and
aligned-spin templates both, we only consider the contribution of the dominant
$l=|m|=2$ waveform multipoles. This approximation has the additional benefit
of combining the dependence of the waveforms on inclination, polarization
and sky location angles, as well as on distance, into the luminosity
or {\it effective} distance. This quantity only appears as an overall scaling
factor, and therefore only affects signal strength~\cite{Sathyaprakash:2009xs}.
}, by sampling the SNR $\rho\in\{20,30,50,70\}$. Our choice of parameters here
is motivated by two factors: (i) previous studies of the signatures of NS tidal
effects on gravitational waves~\cite{FoucartEtAl:2011,Foucart:2013psa,
Foucart:2014nda} (which suggest that necessary conditions for the observation
of tidal effects with aLIGO include high SNRs and a low-mass spinning companion
BH); and (ii) technical constraints of our chosen LEA+ model~\cite{Lackey:2013axa}.
At design sensitivity, if we expect $10-300$ NSBH detections a 
year~\cite{Abadie:2010cfa}, {\it and} if BH mass values are uniformly likely
up to $\sim 35M_\odot$~\cite{LIGOVirgo2016a}, we can expect to detect $0.3-7$
disruptive NSBH mergers a year with $\rho\geq 20$, $0.07-2$ a year with
$\rho\geq 30$, and $0.04-1$ a year with $\rho\geq 70$. Therefore, the parameter
range spanned by our injections represents a physically interesting class of
systems that is {\it also} likely observable in the near future. 
For our Bayesian priors, we choose uniform distributions for both component
masses and black hole spin: $\mbh\in[1.2,25]M_\odot$; $\mns\in[1.2,3]M_\odot$;
and $-0.75\leq \chibh\leq +0.75$.
% \prayush{FIXME}

As an illustration, in Fig.~\ref{fig:SingleSystemEtaPDFvsSNR} we show the
probability distribution for binary mass ratio $\eta$ recovered for an NSBH
injection with $\mns=1.35M_\odot$, $\chins=0$, $\mbh=5.4M_\odot$, $\chibh=+0.5$
and $\lambdans=2000$, with the SNR ranging from $\rho=20$ (left) to
$\rho=50$ (right). In each panel, both the {\it true} and the {\it 
recovered} (median) values of $\eta$ are marked. The effect of ignoring tidal
corrections in templates manifests as a systematic shift of the measured $\eta$
value away from its true value. The associated {\it systematic} bias/error is
measured by the difference between the measured and true $\eta$ values. Darker
shading of the probability distributions marks the $90\%$ credible interval,
whose width $(\Delta\eta)^{90.0\%}$ is a direct measure of the
{\it statistical} measurement uncertainty/error\footnote{We generalize the
notation $(\Delta X)^{90.0\%}$ to mean the $90\%$ credible interval width
for the measured source parameter $X$.}.
% 
We see clearly that even when the signal is moderately loud, with $\rho=20$,
statistical errors dominate over systematics for $\eta$. As we turn up the SNR
further, we find that the two error sources become comparable at $\rho\sim 30$,
and systematic errors dominate finally when $\rho\simeq 50$.

\textcolor{gray}{%
Next, to get a better understanding of how {\it precisely} we measure NSBH
parameters using BBH templates, we show $90\%$ credible intervals associated
with NSBH mass and spin measurements in Fig.~\ref{fig:CIWidths90_Lambda_SNR}.
The three panels correspond to $\mchirp$ (top), $\eta$ (middle), and $\chibh$
(bottom), and show the width of these credible intervals $(\Delta X)^{90\%}$
as a function of BH mass/spin (within each sub-panel), and NS properties, i.e.
$\lambdans$ (downwards in each column)~\footnote{We restrict NS mass to
$1.35M_\odot$ and its spin to zero. Varying its tidal deformability $\lambdans$
does not significantly change the measurement uncertainties for non-tidal
binary parameters, as is evident from comparing the two rows in each panel of
Fig.~\ref{fig:CIWidths90_Lambda_SNR}.}.
% 
From the left-most column, we find that: (i) at $\rho=20, \mchirp$ is already
measured remarkably well - to a precision of $0.16\%$ of its true value, and
(ii) so is $\chibh$. (iii) Mass ratio $\eta$ is determined more loosely,
with $\gtrsim 25\%$ uncertainty. If the signal is even louder ($\rho\geq 30$),
all three measurements gain further precision, with $\eta$ errors shrinking down
to single-digit percents of its true value.
% 
We remind ourselves that this {\it precision}, however, is only
meaningful so long as the measurement is {\it accurate} to begin with. Due to
unmodeled tidal effects, parameter measurements performed on NSBH signals with
BBH templates will have systematic biases. If these biases are too large,
using non-tidal BBH templates should severely impair our inferencing ability.
In order to quantify the relevance of tidal signatures, we define $\arr_X$ as
the ratio between systematic biases and statistical uncertainties associated
with the measurement of parameter $X$. If $\arr_X\gtrsim 1$, incorporating
tidal effects in inspiral and merger modeling would non-trivially improve our
estimation of parameter $X$ from NSBH signals.
% 
% there are physical effects that have not been
% incorporated in our (BBH) search templates which we use here to decipher NSBH
% signals. Therefore, we cannot know the {\it accuracy} of our parameter
% measurements unless we know how large the systematic biases due to an
% incomplete template model are. To quantify this, we find it useful to define
% $\arr_X$, the ratio of the systematic biases induced by unmodeled tidal effects in
% templates, to the statistical uncertainties associated with the measurement
% itself. If $\arr_X\gtrsim 1$, including the effects of NS tidal distortion
% (during inspiral) and possible disruption (close to merger) would be imperative
% to obtain {\it accurate} estimates of source masses and spins from observed GW
% signals.}
}

\textcolor{blue}{%
Credible intervals $(\Delta X)^{90\%}$ measure the precision with which a 
quantity $X$ can be measured. We show credible intervals for
$X=\{\mchirp,\eta,\chibh\}$ in Appendix~\ref{as1:illustrations}. This {\it 
precision}, however, is only meaningful so long as the measurement is {\it
accurate} to begin with. Due to unmodeled tidal effects, parameter measurements
performed on NSBH signals using BBH templates will have systematic biases. If
these biases are too large, using non-tidal BBH templates should severely impair
our
inferencing ability. In order to quantify the relevance of tidal signatures,
we define $\arr_X$ as the ratio between systematic biases and statistical
uncertainties associated with the measurement of parameter $X$. If
$\arr_X\gtrsim 1$, incorporating tidal effects in inspiral and merger modeling
would non-trivially improve our estimation of parameter $X$ from NSBH
signals.
}

We first calculate the ratio of errors $\arr_{\mchirp}$ , and show it in
Fig.~\ref{fig:TN_chirpMassBias_vs_Lambda_SNR}. $\mchirp$ is the mass combination
that affects at leading order the GW strain emitted
by compact binaries as they spiral in, and is therefore determined the most
precisely. From the left-most column of the figure, we find that even at $\rho=30$, 
the systematic bias in $\mchirp$ measurement is much smaller than its statistical
uncertainty. For signals with $\rho\leq 30$, therefore, we are justified in using
BBH templates to estimate binary chirp mass from NSBH signals. For louder and less
realistic SNRs (say $\rho=50$), we find that $\arr$ can become comparable to unity
if additionally: (i) the BH has a prograde spin $\chibh\gtrsim 0.4$, {\it and} (ii)
the true tidal deformability of the NS is large enough, s.t. $\lambdans \gtrsim 1000$.
% 
It is only at SNRs as high as $\rho\simeq70$ that the systematic biases for $\mchirp$
exceed the underlying statistical uncertainty to become the dominant source of
errors.
% 
We conclude that only for $\rho\gtrsim 50-70$ do we need to include in our templates
terms that capture the effect of neutron star's structural dynamics on emitted GWs.
For lower SNRs, improvements in template model will be washed out by the statistical
measurement uncertainty for $\mchirp$.
% 
Lastly, we note that $\arr$ is always positive for $\mchirp$, suggesting that
it is always over-estimated.
This is understandable since the tidal deformation of NSs close to merger reduces
the GW signal power at high frequencies, which would make the resulting signal
resemble a BBH signal of higher mass (and therefore lower merger frequency).

Next, in Fig.~\ref{fig:TN_EtaBias_vs_Lambda_SNR}, we show the ratio of
measurement errors $\arr$ for the symmetric mass-ratio $\eta$. We immediately
observe that the measured (median) $\eta$ is always lowered below its true
value due to the lack of $\lambdans$-dependent terms in the filter template
model. This bias, similar to the $\mchirp$ bias, reduces the merger frequency
for BBH templates, in order to better match the relatively quiet merger and
ringdown of NSBHs. 
% 
At $\rho=30$, the systematic bias in $\eta$ measurement stays mostly around
$10-50\%$ of its statistical measurement uncertainty. For the sole case of a
very deformable NS with $\lambdans=2000$, can the effect of missing tidal pieces
in the template model become comparable to that of noise (which is usually
more restrictive on measurements).
% 
For a still stronger signal with $\rho=50$, we find that when the following
conditions are fulfilled, the measurement of $\eta$ is unreliable due to
template biases: (a) BH mass $\mbh\leq 5M_\odot$, (b) BH spin
$\chibh\gtrsim +0.4$, and (c) $\lambdans\gtrsim 1500$. Even under more
moderate restrictions on BH and NS parameters, we find that $\rho=50$ is 
loud enough to motivate the use of tidal-modeled templates. This observation
is further strengthened if we divert our attention to the third column in
Fig.~\ref{fig:TN_EtaBias_vs_Lambda_SNR} that presents
the case for even higher SNRs ($\rho=70$).

Moving on from mass to spin parameters, we now consider the measurement of spin
angular momentum of the BH $\chibh$. The ratio of the systematic bias introduced into
and the statistical uncertainty associated with $\chibh$ measurement is shown in
Fig.~\ref{fig:TN_BHspinBias_vs_Lambda_SNR}. The presentation of information in this 
figure is identical to that in Fig.~\ref{fig:TN_chirpMassBias_vs_Lambda_SNR}
and~\ref{fig:TN_EtaBias_vs_Lambda_SNR}. A diverging colormap is used because both 
extremes of the colorbar range point to large systematic biases, while its zero (or
small) value lies in the middle. For the lowest considered SNR $\rho=30$, $\chibh$
bias is negligible, being below $50\%$ of its statistical measurement uncertainty.
For the most deformable NS structure {\it and} with a low-mass BH, the statistical
bias in $\chibh$ does become an important error. This is furthered at higher SNR, 
considering $\rho=50$ next (middle column of Fig.~\ref{fig:TN_BHspinBias_vs_Lambda_SNR}).
We find that for low-mass BHs (with masses below $4.5M_\odot$), the systematic 
measurement bias for BH spin exceeds its statistical uncertainty to become the 
dominant source of error. Not surprisingly, the systematic bias at both spin 
extremes pushes towards milder spins, since the prior excludes any more extreme
spins than $[-0.75, +0.75]$ and that pushes the median of the posterior inwards.
However as the signal's $\lambdans$ is increased from $500\rightarrow 2000$,
low-mass BH-NS binaries with large spins on the BH show very large systematic biases
in spin values, that become larger than the statistical uncertainty for $\rho\geq 30$
and reach up to $4\times$ the same quantity as $\rho\rightarrow 70$.

Summarizing these results, we find that irrespective of system parameters, below a
signal-to-noise ratio of $30$, our measurements of mass and spin parameters of 
astrophysical BHNS binaries will remain limited by the intrinsic uncertainty due to 
instrument noise, and do not depend on whether we include tidal effects in template
models. However, when the signal-to-noise ratio exceeds $30$ the systematic bias in
binary mass and spin measurements become comparable to and exceed the uncertainty
due to noise. Of the different parameters considered, we find that the measurement 
of $\eta$ degrades worst (in a relative-error sense) amongst all other parameters
of BHNS binaries, due to the use of BH-BH waveforms in deciphering an NSBH signal.

@@

>>>>

Past (and future) efforts with Advanced LIGO have used (or plan to use) BBH

@@

We inject LEA+ NSBH signals into zero noise, and run an MCMC sampler on
them using equivalent BBH templates (same model, tidal terms $\rightarrow 0$).
We fix $\mns=1.35M_\odot$ and $\chins=0$, and explore a range of NS
equations of state via the single tidal deformability parameter
$\lambdans\in\{500, 800, 1000, 1500, 2000\}$. Our injections also span a
rectangular grid in the BH parameter space, with vertices at
$q\in\{2,3,4,5\}$, i.e.
$\mbh\in\{2.7M_\odot, 4.05M_\odot, 5.4M_\odot, 6.75M_\odot\}$, and BH spins
$\chibh\in\{-0.5, 0, +0.5, +0.75\}$. 
Finally, we sample all other source-related parameters that determine the
signal strength but not character\footnote{For aligned-spin signals and
aligned-spin templates both, we only consider the contribution of the dominant
$l=|m|=2$ waveform multipoles. This approximation has the additional benefit
of combining the dependence of the waveforms on inclination, polarization
and sky location angles, as well as on distance, into the luminosity
or {\it effective} distance. This quantity only appears as an overall scaling
factor, and therefore only affects signal strength~\cite{Sathyaprakash:2009xs}.
}, by sampling the SNR $\rho\in\{20,30,50,70\}$. Our choice of injection
parameters here
is motivated by two factors: (i) previous studies of the signatures of NS tidal
effects on gravitational waves~\cite{FoucartEtAl:2011,Foucart:2013psa,
Foucart:2014nda} (which suggest that necessary conditions for the observation
of tidal effects with aLIGO include high SNRs and a low-mass spinning companion
BH); and (ii) technical constraints of our chosen LEA+ model~\cite{Lackey:2013axa}.
At design sensitivity, if we expect $10-300$ NSBH detections a 
year~\cite{Abadie:2010cfa}, {\it and} if BH mass values are uniformly likely
up to $\sim 35M_\odot$~\cite{LIGOVirgo2016a}, we can expect to detect $0.3-7$
{\it disruptive} NSBH mergers a year with $\rho\geq 20$, $0.07-2$ a year with
$\rho\geq 30$, and $0.04-1$ a year with $\rho\geq 70$. Therefore, the parameter
range spanned by our injections represents a physically interesting class of
systems that is {\it also} likely observable in the near future. 
For our Bayesian priors, we choose uniform distributions for both component
masses and black hole spin: $\mbh\in[1.2,25]M_\odot$; $\mns\in[1.2,3]M_\odot$;
and $-0.75\leq \chibh\leq +0.75$.
% \prayush{FIXME}

As an illustration, in Fig.~\ref{fig:SingleSystemEtaPDFvsSNR} we show 
recovered probability distributions for binary mass ratio $\eta$, for NSBH
injections with $\mns=1.35M_\odot$, $\chins=0$, $\mbh=5.4M_\odot$, $\chibh=+0.5$
and $\lambdans=2000$, with the SNR ranging from $\rho=20$ (left) to
$\rho=50$ (right). In each panel, both the {\it true} and the {\it 
recovered} (median) values of $\eta$ are marked. The effect of ignoring tidal
corrections in templates manifests as a systematic shift of the measured $\eta$
value away from its true value. The associated {\it systematic} bias/error is
measured by the difference between the measured and true $\eta$ values. Darker
shading of the probability distributions marks the $90\%$ credible interval,
whose width $(\Delta\eta)^{90.0\%}$ is a direct measure of the
{\it statistical} measurement uncertainty/error\footnote{We generalize the
notation $(\Delta X)^{90.0\%}$ to mean the $90\%$ credible interval width
for any measured source parameter $X$.}.
% 
We see clearly that even when the signal is moderately loud, with $\rho=20$,
statistical errors dominate over systematics for $\eta$. As we turn up the SNR
further, we find that the two error sources become comparable at $\rho\sim 30$,
and systematic errors dominate finally when $\rho\simeq 50$.

\textcolor{gray}{%
Let us first delve into statistical errors. In
Fig.~\ref{fig:CIWidths90_Lambda_SNR}, we show how {\it precisely} can we
measure NSBH parameters $X=\{\mchirp,\eta,\chibh\}$ using BBH templates.
The three panels correspond to $\mchirp$ (top), $\eta$ (middle), and $\chibh$
(bottom), and show the width of these credible intervals $(\Delta X)^{90\%}$
as a function of BH mass/spin (within each sub-panel), and NS properties, i.e.
$\lambdans$ (downwards in each column)~\footnote{We restrict NS mass to
$1.35M_\odot$ and its spin to zero. Varying its tidal deformability $\lambdans$
does not significantly change the measurement uncertainties for non-tidal
binary parameters, as is evident from comparing the two rows in each panel of
Fig.~\ref{fig:CIWidths90_Lambda_SNR}.}.
% 
From the left-most column, we find that: (i) at $\rho=20, \mchirp$ is already
measured remarkably well - to a precision of $0.16\%$ of its true value, and
(ii) so is $\chibh$. (iii) Mass ratio $\eta$ is determined more loosely,
with $\gtrsim 25\%$ uncertainty. If the signal is even louder ($\rho\geq 30$),
all three measurements gain further precision, with $\eta$ errors shrinking down
to single-digit percents of its true value.
% % 
% We remind ourselves that this {\it precision}, however, is only
% meaningful so long as the measurement is {\it accurate} to begin with.
% We define $\arr_X$ as the ratio between systematic and statistical
% errors associated with the measurement of parameter $X$,
% \begin{equation}\label{eq:arr}
% \arr_X = \dfrac{(X^\mathrm{Median} - X^\mathrm{Injected})}{(\Delta X)^{90\%}},
% \end{equation}
% in order to compare the relative importance of both. Only when
% $|\arr_X| < 1$ can we hope that ignoring tidal effects in our templates
% will not hamper the measurement of non-tidal parameters from NSBH signals.
% Due to
% unmodeled tidal effects, parameter measurements performed on NSBH signals with
% BBH templates will have systematic biases. If these biases are too large,
% using non-tidal BBH templates should severely impair our inferencing ability.
% 
% there are physical effects that have not been
% incorporated in our (BBH) search templates which we use here to decipher NSBH
% signals. Therefore, we cannot know the {\it accuracy} of our parameter
% measurements unless we know how large the systematic biases due to an
% incomplete template model are. To quantify this, we find it useful to define
% $\arr_X$, the ratio of the systematic biases induced by unmodeled tidal effects in
% templates, to the statistical uncertainties associated with the measurement
% itself. If $\arr_X\gtrsim 1$, including the effects of NS tidal distortion
% (during inspiral) and possible disruption (close to merger) would be imperative
% to obtain {\it accurate} estimates of source masses and spins from observed GW
% signals.}
}

\textcolor{blue}{%
Credible intervals $(\Delta X)^{90\%}$ measuring the precision with which
$X=\{\mchirp,\eta,\chibh\}$ can be measured, are discussed in detail in
Appendix~\ref{as1:illustrations}.
}
We remind ourselves that this {\it precision} is only meaningful so long as the
measurement is {\it accurate} to begin with. Therefore, we define $\arr_X$ as
the ratio between systematic and statistical errors associated with the
measurement of parameter $X$,
\begin{equation}\label{eq:arr}
\arr_X = \dfrac{(X^\mathrm{Median} - X^\mathrm{Injected})}{(\Delta X)^{90\%}},
\end{equation}
in order to compare the relative importance of both. Only when
$|\arr_X| < 1$ can we hope that ignoring tidal effects in our templates
will not hamper the measurement of non-tidal parameters from NSBH signals.
% 
We start with calculating $\arr_{\mchirp}$, and show it in
Fig.~\ref{fig:TN_chirpMassBias_vs_Lambda_SNR}. $\mchirp$ is the leading order
mass combination that affects the GW strain emitted by compact binaries as they
spiral in, and is therefore determined the most precisely. We notice
immediately that for $\rho\leq 30$ the systematics are well under control
and so we can obtain reliable chirp mass estimates for NSBH signals using BBH
templates.
% 
For louder and less likely SNRs ($\rho\simeq 50$), we show that
$\arr_{\mchirp}$ can become comparable to unity, but only if the BH has
prograde spin $\chibh\gtrsim 0.4$, {\it and} the true NS tidal deformability
is large enough, s.t. $\lambdans \gtrsim 1000$.
% 
We therefore conclude that only for very loud signals, with
$\rho\gtrsim 50-70$, will the inclusion of tidal terms in our template
models improve our $\mchirp$ estimation. For lower SNRs, inclusion of new
physical content in templates will instead get washed out by detector noise.
% 
In addition to everything, we also note that $\arr_{\mchirp}\geq 0$ always,
i.e. $\mchirp$ is always being over-estimated. This is to be expected since
the tidal deformation and disruption of NSs close to merger reduces GW signal
power at high frequencies, making the resulting signal resemble a BBH signal of
lower merger frequency - and therefore of higher mass.

Next, in Fig.~\ref{fig:TN_EtaBias_vs_Lambda_SNR}, we show the ratio of
measurement errors $\arr_\eta$ for the symmetric mass-ratio. We straight-away
notice that, unlike for $\mchirp$, the measured (median) value of $\eta$ is
always {\it lower} than its true value due to the lack of $\lambdans$-dependent
terms in filter templates. This also is so because templates with $\arr_\eta<0$
will have a lower merger frequency than the one with $\arr_\eta=0$, and will
therefore better fit a disruptive NSBH merger.
% 
Going through the figure from left to right, we find that for realistic
SNRs ($\rho\leq 30$) the systematics remain below statistical errors for
$\eta$ measurement. The worst case is for the most deformable NSs
($\lambdans = 2000$), but even for them systematics in $\eta$ are $2\times$
smaller than the statistical measurement errors.
% 
Moving to louder signals with $\rho\simeq 50$, we find that for binaries of
fairly deformable NSs ($\lambdans\gtrsim 1500$), and low-mass BHs
($\mbh\leq 5M_\odot$) that have prograde spins ($\chibh\gtrsim +0.4$), our
measurement of mass-ratio can be seriously compromised by ignoring tidal
physics in template models. 
% 
This pattern is continued to even higher SNRs, as we can see from
Fig.~\ref{fig:TN_EtaBias_vs_Lambda_SNR}. We therefore conclude that, even if
under moderate restrictions on BH and NS parameters, $\rho=50$ is loud enough
to motivate the use of tidal templates in aLIGO data analyses.

Moving on from mass to spin parameters, we now consider the measurement of BH
spin angular momentum $\chibh$. The ratio of systematic and statistical errors
associated with $\chibh$ measurement is shown in
Fig.~\ref{fig:TN_BHspinBias_vs_Lambda_SNR}. The presentation of information in this 
figure is identical to that of Fig.~\ref{fig:TN_chirpMassBias_vs_Lambda_SNR}
and~\ref{fig:TN_EtaBias_vs_Lambda_SNR}. A diverging colormap is used so that both 
extremes of the colorbar range point to large systematic biases, while its zero (or
small) value lies in the middle.
% 
For the lowest considered SNR ($\rho=30$), $\chibh$ bias is about $2\times$
smaller than the statistical measurement uncertainty and is therefore mostly
negligible. Both can become comparable only when we have the most deformable NSs
in orbit around low-mass BHs. 
% 
Moving to higher SNRs, at $\rho\simeq50$ we find that systematics in $\chibh$
measurement begin to dominate for $\mbh\leq 4.5M_\odot$.
This suggests that we would need tidal templates to accurately
characterize astrophysical mass-gap violating NSBH binaries.
% 
At even higher SNRs, the systematics can completely dominate BH spin
measurement.
% 
From Fig.~\ref{fig:TN_BHspinBias_vs_Lambda_SNR} we also note that when signal
spins are the largest, $\chibh\times\arr_{\chibh}<0$. This is to be
expected because the median of the recovered posterior distribution for $\chibh$
can only get pushed inwards from the boundaries.

Summarizing these results, we find that irrespective of system parameters, below a
signal-to-noise ratio of $30$, our measurements of mass and spin parameters of 
astrophysical NSBH binaries will remain limited by the intrinsic uncertainty due to 
instrument noise, and do not depend on whether we include tidal effects in template
models. However, when the signal-to-noise ratio exceeds $30$ the systematic bias in
binary mass and spin measurements become comparable to and can exceed the
uncertainty due to noise. Of the different parameters considered, we find that
amongst all non-tidal parameters, the measurement of $\eta$ degrades worst (in a 
relative-error sense) due to the use of BBH templates in deciphering an NSBH
signal.

@@

Let us first delve into statistical errors. In
Fig.~\ref{fig:CIWidths90_Lambda_SNR}, we show how {\it precisely} can we
measure NSBH parameters $X=\{\mchirp,\eta,\chibh\}$ using BBH templates.
The three panels correspond to $\mchirp$ (top), $\eta$ (middle), and $\chibh$
(bottom), and show the width of these credible intervals $(\Delta X)^{90\%}$
as a function of BH mass/spin (within each sub-panel), and NS properties, i.e.
$\lambdans$ (downwards in each column)~\footnote{We restrict NS mass to
$1.35M_\odot$ and its spin to zero. Varying its tidal deformability $\lambdans$
does not significantly change the measurement uncertainties for non-tidal
binary parameters, as is evident from comparing the two rows in each panel of
Fig.~\ref{fig:CIWidths90_Lambda_SNR}.}.
% 
From the left-most column, we find that: (i) at $\rho=20, \mchirp$ is already
measured remarkably well - to a precision of $0.16\%$ of its true value, and
(ii) so is $\chibh$. (iii) Mass ratio $\eta$ is determined more loosely,
with $\gtrsim 25\%$ uncertainty. If the signal is even louder ($\rho\geq 30$),
all three measurements gain further precision, with $\eta$ errors shrinking down
to single-digit percents of its true value.
% % 
% We remind ourselves that this {\it precision}, however, is only
% meaningful so long as the measurement is {\it accurate} to begin with.
% We define $\arr_X$ as the ratio between systematic and statistical
% errors associated with the measurement of parameter $X$,
% \begin{equation}\label{eq:arr}
% \arr_X = \dfrac{(X^\mathrm{Median} - X^\mathrm{Injected})}{(\Delta X)^{90\%}},
% \end{equation}
% in order to compare the relative importance of both. Only when
% $|\arr_X| < 1$ can we hope that ignoring tidal effects in our templates
% will not hamper the measurement of non-tidal parameters from NSBH signals.
% Due to
% unmodeled tidal effects, parameter measurements performed on NSBH signals with
% BBH templates will have systematic biases. If these biases are too large,
% using non-tidal BBH templates should severely impair our inferencing ability.
% 
% there are physical effects that have not been
% incorporated in our (BBH) search templates which we use here to decipher NSBH
% signals. Therefore, we cannot know the {\it accuracy} of our parameter
% measurements unless we know how large the systematic biases due to an
% incomplete template model are. To quantify this, we find it useful to define
% $\arr_X$, the ratio of the systematic biases induced by unmodeled tidal effects in
% templates, to the statistical uncertainties associated with the measurement
% itself. If $\arr_X\gtrsim 1$, including the effects of NS tidal distortion
% (during inspiral) and possible disruption (close to merger) would be imperative
% to obtain {\it accurate} estimates of source masses and spins from observed GW
% signals.}
